Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
added more references and images for figures

\section{Pipeline}
We begin with a set of user constraints, which illustrate the general shape of
the roads on the blank canvas. These can be linear or radial, and can be input
as JSON. From these we generate a tensor field, and from that, major and minor
eigenvector fields, which describe the direction stipulated by the constraints
at every point in the area. Finally, based on these eigenvector fields, we
generate seed points from which streamlines are traced across the map. These
streamlines produce the final roads.

@@

\subsection{Seed Placement}\label{seedpoints}
To begin constructing a streamline, one must choose a seed point—--an initial
coordinate in 2D space from which the streamline is traced. In practice, the
matter of carefully choosing seed points is very important in generating an
evenly spaced configuration of roads. We investigated three methods of placing
seed points:
\begin{enumerate}
    \item Random
    \item Furthest-Point
    \item Even Streamline Spacing ($\chi^2$ distribution)
\end{enumerate}

@@

\section{Assessment}
There were two main goals that we set out to achieve with this project. Here we
present a mostly heuristic, slightly quantitative attempt to qualify our
success, using both internal evaluation and comparisons to existing systems
\cite{chen}.

@@

\subsection{Modularity \& Extensibility}
We believe that we were successful in creating a modular system with reusable
parts that is easy to understand, extend, and modify. One way to illustrate
this is by looking at our pipeline (Figure \ref{fig:pipeline}). Each step of
the pipeline has a clear correspondence in the modules that we have written.
We have two modules to deal with constraints, \texttt{Constraint}. To transform
constraints to maps, we have written \texttt{TensorField} and \texttt{Tensor}
modules, the latter of which performs operations on tensors including
eigenvector calculations, as well as \texttt{Streamline}, which has the ability
to calculate seed points and trace lines.

We also created several generally useful modules, including \texttt{Vector2},
which performs basic operations on 2-dimensional vectors and
\texttt{NearestNeighbor}, which defines a type class for a structure that can
store \texttt{Vector2}s and query for the nearest neighbor, as well as a
bucket-based implementation of such a data structure. To deal with input and
output, we created a \texttt{JSONParser} so that our input can come from any
source that is capable of producing JSON, and an \texttt{SVGWriter}, which
deals with the widely-used file format that produces the output seen in many of
the figures in this paper.

>>>>

\section{Pipeline}\label{sec:pipeline}
We begin with a set of user constraints, which illustrate the general shape of
the roads on the blank canvas. These can be linear or radial, and can be input
as JSON. From these we generate a tensor field, and from that, major and minor
eigenvector fields, which describe the direction stipulated by the constraints
at every point in the area. Finally, based on these eigenvector fields, we
generate seed points from which streamlines are traced across the map. These
streamlines produce the final roads.

@@

\subsection{Seed Placement}\label{sec:seedpoints}
To begin constructing a streamline, one must choose a seed point—--an initial
coordinate in 2D space from which the streamline is traced. In practice, the
matter of carefully choosing seed points is very important in generating an
evenly spaced configuration of roads. We investigated three methods of placing
seed points:
\begin{enumerate}
    \item Random
    \item Furthest-Point
    \item Even Streamline Spacing ($\chi^2$ distribution)
\end{enumerate}

@@

\section{Assessment}
We set out to achieve two goals: modularity and expressiveness. In this section
we will examine the extent to which these goals were achieved.

\subsection{Modularity and Extensibility}
In Section \ref{sec:seedpoints}, we outlined three methods of seedpoint
placement: random, furthest-point, and $\chi^2$ even spacing. All three
are implemented by functions in the \texttt{Streamline} module, and follow a
similar template. Extending this module with other methods is as simple as
implementing a new function with the same type signature as
\texttt{placeSeeds}, adding a new value constructor to the datatype
\texttt{PlacementMethod}, and adding a new case to the function
\texttt{placeStreamlines} to match the new data constructor. The purity of
functions in a language such as Haskell makes it simple to drop in replacements
for existing functions because one does not have to consider possible side
effects, but only the types of the inputs and output.

In order to detect intersections between streamlines as they are traced, we
defined the \texttt{NearestNeighbor} module to implement a data structure which
stored a set of 2D points and could be queried to determine which of the stored
points was closest to the query point. This is implemented using a type
family, with an instance utilizing a blocked 2D array implementation. This
instance was sufficient for testing purposes, but is currently the performance
bottleneck in streamline tracing. A new instance of the \texttt{Storage}
type family could easily be defined in accordance with the type signature to
provide a more efficient representation. For example, a k-d tree instance of
the type family could offer higher performance. This well-defined abstraction
boundary makes this aspect of our pipeline very easily extensible.

\subsection{Expressiveness}
As our work was not a complete reimplementation of the system described in
\cite{chen}

@@

\subsection{Modularity \& Extensibility}
